---
title: "t-SNE Experiments"
output: html_notebook
---

Data side:
(initial) 1034 obs for original distance matrix and clustering (gap/no gap, nacost 0/2) 
From readFile.R file 
reads the input data from the ./data/input/ directory and saves the following .RData Files
sequences.RData - TraMineR sequences filesGap.seq and filesNoGap.seq
age.RData, gender.RData - age and gender
distances.RData - the OM matrix for all 12 cases
in ./data directory
```{r}
devtools::load_all("C:/Users/AlinaLazar/Documents/__18spring/research/jdiq/wholetraveler")
#devtools::install("C:/Users/AlinaLazar/Documents/__18spring/research/jdiq/wholeTraveler")
#library(wholeTraveler))
data(package="wholetraveler")

```


```{r}
pathI = paste0(system.file(package = "wholetraveler"), "/extdata/input/")
pathO <- paste0(system.file(package = "wholetraveler"), "/extdata/output/")
readInputData(pathI,pathO)
```
From clusteringAssignmentInitial.R
save cluster assignments for k = 2,3,4,5 – to ./data/clusterAssignInitial/
```{r}
pathO <- paste0(system.file(package = "wholetraveler"), "/extdata/output/clusterAssignInitial/")
clustAssigInitial(mcdist.om1,pathO)
```

(tsne) 1034 obs for tsne transformation, "after tSNE" distance matrix and clustering --->
save after tsne distance matrix tsneDistances.RData
save cluster assignment for k = 2,3,4,5 – to ./data/clusterAssignTsne/
```{r}
pathI <- paste0(system.file(package = "wholetraveler"), "/extdata/input/tsnePy1000/")
pathO <- paste0(system.file(package = "wholetraveler"), "/extdata/output/clusterAssigTsnePy1000/")
inputFile<-paste0(pathI,"tsneResults90.RData")
load(inputFile)
clustAssigTsne(disttsne,pathO)
```




Figures:
1.	sequence plots (distribution and individual) for "initial" and "tsne"
```{r}
pathI<-paste0(system.file(package = "wholetraveler"), "/extdata/output/")
pathP<-"./plots/tsnePy1000/seqPlots/"
ifelse(!dir.exists(file.path(pathP)), dir.create(file.path(pathP),recursive=TRUE), FALSE)
allClusterSeqPlots(pathI,pathP,2,5)
```

```{r}
pathI<-paste0(system.file(package = "wholetraveler"), "/extdata/output/")
pathP<-"./plots/tsnePy1000/domainSeqPlots/"
ifelse(!dir.exists(file.path(pathP)), dir.create(file.path(pathP),recursive=TRUE), FALSE)
allDomainClustSeqPlots(pathI,pathP,2,5)
```

2.	scatter plots of 12 experiments using kPCA, MDS, SE, and tSNE (perplexity = 90, max_iter=1000), color code by "initial" cluster assignment (k=4)
```{r}
path1 <- paste0(system.file(package = "wholetraveler"), "/extdata/output/clusterAssignInitial/")
path2 <- paste0(system.file(package = "wholetraveler"), "/extdata/input/dimRed/")
pathO <- "./plots/scatterPlotsDimRed/"
ifelse(!dir.exists(file.path(pathO)), dir.create(file.path(pathO),recursive=TRUE), FALSE)
scatterPlotDimRed(path1,path2,pathO)

```

3.	scatter plots of hyperparameter choices for tSNE (perplexity = 10~ 100); color code by "initial" cluster assignment (k=4). 3 rounds tsneR 	tsnePy500		tsnePY1000
```{r}
path1 <- paste0(system.file(package = "wholetraveler"), "/extdata/output/clusterAssignInitial/")
path2 <- paste0(system.file(package = "wholetraveler"), "/extdata/input/tsnePy1000/")
pathO <- "./plots/scatterPlotsPerplexity/"
ifelse(!dir.exists(file.path(pathO)), dir.create(file.path(pathO),recursive=TRUE), FALSE)
scatterPlotPerplexity(path1,path2,pathO)
```

4.	scatter plots of "initial" + "tsne" cluster assignments (k = 2, 3, 4, 5), using perplexity = 30
```{r}
path1 <- paste0(system.file(package = "wholetraveler"), "/extdata/output/clusterAssignInitial/")
path2 <- paste0(system.file(package = "wholetraveler"), "/extdata/output/clusterAssignTsnePy500/")
path3 <- paste0(system.file(package = "wholetraveler"), "/extdata/input/TsnePy500/")
pathO <- "./plots/scatterPlotsTsne/"
ifelse(!dir.exists(file.path(pathO)), dir.create(file.path(pathO),recursive=TRUE), FALSE)
scatterPlotsTsne(path1,path2,path3,pathO)

```

5.	scatter plots with age (and most frequent state) brush + "initial" cluster assignment, using perplexity = 30
```{r}

```

6.	age bar plots (initial, and tsne)
```{r}

```

7.	for each of the NAcost+gap case, color code the binary and nominal scatter plot by combined "initial" cluster assignment; using perplexity = 30.
```{r}
path1 <- paste0(system.file(package = "wholetraveler"), "/extdata/output/clusterAssignInitial/")
path2 <- paste0(system.file(package = "wholetraveler"), "/extdata/input/tsnePy500/")
pathO <- "../plots/scatterPlotsPerplexity/"
scatterPlotPerplexityCombined(path1,path2,pathO)
```

8.	asw and pbc plots (done already, no need to change).
```{r}

```

